TEMPERATURES AND METALLICITIES OF M DWARFS IN THE APOGEE SURVEY

### 2019-08-22 paper/draft.tex
tweaks

Compared to the \citet{Mann:2015} and \citet{Boyajian:2012} color-metallicity derived temperatures, both ASPCAP and \cannon\ temperatures show similar scatters of $\sim60\,$K, but are offset by a constant.
We find \cannon\ to be in better agreement with \citet{Mann:2015} and \citet{Boyajian:2012}, with ASPCAP overestimating $\teff$ on average $\sim110-140\,$K, and \thecannon\ underestimating $\teff$ on average by $\sim10-20\,$K, with the largest deviation in the latter at the lowest and highest Teffs.

@@

As expected, the Toomre diagram in Figure \ref{fig:toomre} shows that higher metallicity sources in the sample are concentrated in low velocity space corresponding roughly to the thin disk population; while the thick disk population contains a higher concentration of lower metallicity sources. Separating the two populations into separate histograms (also shown in Figure \ref{fig:toomre}), we find that thick disk sources are marginally more metal poor than thin disk sources, with the mean $\pm$ standard deviation of $\feh=0.00\pm0.17\,$dex for the thin disk distribution, and $\feh=-0.14\pm0.19\,$dex for the thick disk distribution.
Metallicities of the two populations from ASPCAP show a similar distribution, with the mean $\pm$ standard deviation being $\mh=-0.16\pm0.16\,$dex for thin disk sources and $\mh=-0.23\pm0.17\,$dex for thick disk sources.

>>>>

Compared to the \citet{Mann:2015} and \citet{Boyajian:2012} color-metallicity derived temperatures, both ASPCAP and \cannon\ temperatures show similar scatters of $\sim60\,$K, but are offset by a constant.
We find \cannon\ to be in better agreement with \citet{Mann:2015} and \citet{Boyajian:2012}, with ASPCAP overestimating $\teff$ on average $\sim110-140\,$K, and \thecannon\ underestimating $\teff$ on average by $\sim10-20\,$K, with the largest deviation in the latter at the lowest and highest $\teff$s.

@@

As expected, the Toomre diagram in Figure \ref{fig:toomre} shows that higher metallicity sources in the sample are concentrated in low velocity space corresponding roughly to the thin disk population; while the thick disk population contains a slightly higher concentration of lower metallicity sources. Separating the two populations into separate histograms (also shown in Figure \ref{fig:toomre}), we find that thick disk sources are marginally more metal poor than thin disk sources, with the mean $\pm$ standard deviation of $\feh=0.00\pm0.17\,$dex for the thin disk distribution, and $\feh=-0.14\pm0.19\,$dex for the thick disk distribution.
Metallicities of the two populations from ASPCAP show a similar distribution, with the mean $\pm$ standard deviation being $\mh=-0.16\pm0.16\,$dex for thin disk sources and $\mh=-0.23\pm0.17\,$dex for thick disk sources.
